Results

### 2018-11-26 Manuscript_draft/Results.Rmd
Brassicaceae ggplot Selfing_rate

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
library(plotrix)
library(dplyr)
library(ggfortify)
library(ggplot2)
library(stats)
library(cluster)
library(MASS)
#load environment
load("myEnvironment_mantel.RData")
```

@@

The number of possible combinations with 10 species (multiplied by two because is in both directions the treatments A to B and B to A):

$$(\frac{10}{2})=\frac{10!}{2!*(8!)}*2=90 $$

In total we performed 4400 treatments. If we just consider seed set, 2200 treatments including [50% Hp, 100% Hp, hand cross pollination, self pollination, natural selfing (bagged flowers) and apomixis (emasculated flowers)].

@@

\newpage
Now I use non metric multidimensional scaling for all the traits of our species. The traits used are: Stigma_type, Selfing_rate, Pollem_size, Mean_pollen_anther, Mean_ovules, Pollen_ovule_ratio, Anthers, Stigma_length, Stigma_surface (width), Style_length, Style_width, Ovary_width, Ovary_length

@@

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
library(plotrix)
library(dplyr)
library(ggfortify)
library(ggplot2)
library(stats)
library(cluster)
library(MASS)
library(cowplot)
#load environment
load("myEnvironment_mantel.RData")
```

@@

@@

\newpage
Now I use non metric multidimensional scaling for all the traits of our species. The traits used are: Stigma_type, Selfing_rate, Pollen_size, Mean_pollen_anther, Mean_ovules, Pollen_ovule_ratio, Anthers, Stigma_length, Stigma_surface (width), Style_length, Style_width, Ovary_width, Ovary_length

@@

\newpage

Interestignly for Brassicaceae species selfing rates matches pretty well the output of heterospecific pollen effect. Therefore, seems that selfing rates in Brassicaceae species could be a good predictor of foreign pollen effect. When we consider the relatedness of the donors, for instance crosses between families

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
load("Data/all_bra.Rda")
cbPalette <- c("#000000", "#E69F00", "darkturquoise", "deeppink3")
 ggplot(all_bra, aes(x=close_related, y=hp_effect)) + 
  geom_jitter(width=0.1,aes(colour = Pollen_recipient),size=3.5)+
  theme_cowplot()+theme(axis.title.x=element_blank(),
axis.text.x=element_blank(),axis.ticks.x=element_blank(),legend.position = c(0.7, 0.8))+
  scale_x_continuous(limits = c(0.8, 1.35)) +scale_y_continuous("Heterospecific pollen effect")+
   annotate("text", x = c(0.82,0.82), y=c(0.4,2.2), label = c("Low effect","High effect"))+
   geom_hline(yintercept = 1.5)+scale_color_manual(values = cbPalette)+labs(title = "Brassicaceae spp", subtitle = "")
```
